---
title: "534_project_notebook"
author: "NL"
date: "22/01/2020"
output: html_document
---

## Jan 22, 2020 API Selection
Reviewed different APIs, discussed with Jasmine and Chris and chose the Github Events API. 

## Jan 23, 2020 Create R wrapper
Took the online mini course "An Introduction to APIs" https://zapier.com/learn/apis/ and read "Best practices for API packages"  https://httr.r-lib.org/articles/api-packages.html. 

Created R wrapper to access repository events https://developer.github.com/v3/activity/events/#list-repository-events. 


## Jan 24, 2020 Create gitevents package
Created the R package and added the file with R wrapper function to the /R package. 

## Jan 25, 2020 Create DF function
Added a function to create a DF to repo_events file using the parsed data that we get from the get_repo_events function. This is probably a more useable format. 

## Jan 26, 2020 Create labbook stamp function
Added a function to print out events for a repo for a given date. 

## Jan 31, 2020 Documentation and testing
Started unit testing using testthat() on my functions. Also updated DESCRIPTION, LICENSE, manual with help files for my functions, NAMESPACE. Created a skeleton README file. 

## Feb 3, 2020 Complete package and Travis CI
Integrated Jasmine's functions then implemented Travis CI. Also Chris added vignettes. 
```{r }
log <- get_repo_log('nganlyle', '534_project', '2020-02-03'); log
```

## Feb 4, 2020 Complete package and Travis CI
Worked with Jasmine and Chris to plan the demo. Converting the log into html or Rmarkdown does not work well in Rmarkdown environment (freezing) so adjusted the function to return a simple dataframe. 

```{r }
log <- get_repo_log('nganlyle', '534_project', '2020-02-04'); log
```

## Feb 5, 2020 Documentation and demo
Met with Chris and Jasmine to practice the presention. Added Code of Conduct and Contibuting documents to the package. 
```{r }
log <- get_repo_log('nganlyle', '534_project', '2020-02-05'); log

```




```{r }

```




```{r }

```




```{r }

```




```{r }

```




```{r }

```


